---
title: "Presenting outputs"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)

```

## Q1: What is the win rate by Tier and Sub sector ID. Split the above in to FY19 and FY20.

```{r}

#### Reading the data:

library(readr)
library(plyr)
library(ggplot2)

dat <- read_csv("Data.csv")



################################################
################## Q1: #########################
################################################
dat0 <- dat[dat$Stage == 'Closed Won',]


q1 <- with(dat0, ftable(dat0$`Sub Sector ID`,dat0$`Account Tier`))
q1 <- as.data.frame(q1)
colnames(q1) <- c("SubSector","Tier","Freq")
q1$win_percentage <- round((q1$Freq/sum(q1$Freq)*100),1)
q1$label = paste0(sprintf("%.0f", q1$win_percentage), "%")

q1[q1 == 0] <- NA


plot0 <- ggplot(q1, aes(x = factor(SubSector), y = win_percentage, fill = Tier)) +
          geom_bar(position = position_stack(), stat = "identity", width = .7) +
          geom_text(aes(label = label), position = position_stack(vjust = 0.5), size = 3)+
          coord_flip()


plot0 <- plot0 + labs(title = "Win (%) by SubSector and Tier",
                         y="Win(%)", x = "Sub sector ID")





## Subsetting:
dat1 <- dat[dat$Stage == 'Closed Won' & dat$FY == "FY19",]


q1 <- with(dat1, ftable(dat1$`Sub Sector ID`,dat1$`Account Tier`))
q1 <- as.data.frame(q1)
colnames(q1) <- c("SubSector","Tier","Freq")
q1$win_percentage <- round((q1$Freq/sum(q1$Freq)*100),1)
q1$label = paste0(sprintf("%.0f", q1$win_percentage), "%")

q1[q1 == 0] <- NA


plot1 <- ggplot(q1, aes(x = factor(SubSector), y = win_percentage, fill = Tier)) +
          geom_bar(position = position_stack(), stat = "identity", width = .7) +
          geom_text(aes(label = label), position = position_stack(vjust = 0.5), size = 3)+
          coord_flip()


plot1 <- plot1 + labs(title = "Win (%) by SubSector and Tier (FY19)",
                         y="Win(%)", x = "Sub sector ID")

##########################################################################
dat1 <- dat[dat$Stage == 'Closed Won' & dat$FY == "FY20",]


q1 <- with(dat1, ftable(dat1$`Sub Sector ID`,dat1$`Account Tier`))
q1 <- as.data.frame(q1)
colnames(q1) <- c("SubSector","Tier","Freq")
q1$win_percentage <- round((q1$Freq/sum(q1$Freq)*100),1)
q1$label = paste0(sprintf("%.0f", q1$win_percentage), "%")

q1[q1 == 0] <- NA


plot2 <- ggplot(q1, aes(x = factor(SubSector), y = win_percentage, fill = Tier)) +
  geom_bar(position = position_stack(), stat = "identity", width = .7) +
  geom_text(aes(label = label), position = position_stack(vjust = 0.5), size = 3)+
  coord_flip()


plot2 <- plot2 + labs(title = "Win (%) by SubSector and Tier (FY20)",
             y="Win(%)", x = "Sub sector ID")


plot0

library("ggpubr")
figure <- ggarrange(plot1,plot2,ncol = 1, nrow = 2)
figure

```

##Q2:  How many opportunities are open (i.e. not closed lost or closed won) by stage and tier. (e.g. we have x number of opportunities open at stage y for Tier 1)


```{r}
#How many opportunities are open (i.e. not closed lost or closed won) by stage and tier..
#e.g. we have x number of opportunities open at stage y for Tier 1



dat2 <- droplevels(dat[!dat$Stage == "Closed Lost",])
dat2 <- droplevels(dat2[!dat2$Stage == "Closed Won",])




q2 <- with(dat2, ftable(dat2$Stage,dat2$`Account Tier`))
q2 <- as.data.frame(q2)
colnames(q2) <- c("Stage","Tier","Freq")
q2[q2 == 0] <- NA
#q1$win_percentage <- round((q1$Freq/sum(q1$Freq)*100),1)
#q2$label = paste0(sprintf("%.0f", q1$win_percentage), "%")

plot3 <- ggplot(q2, aes(x = factor(Stage), y = Freq, fill = Tier)) +
  geom_bar(position = position_stack(), stat = "identity", width = .7) +
  geom_text(aes(label = Freq), position = position_stack(vjust = 0.5), size = 3.5)+
  coord_flip()

plot3 <- plot3 + labs(title = "Open opportunities by stage and tier",
                      y="Frequency", x = "Stage")
plot3

```

##Q3: What is the average order value (ABC) by Tier and Sub sector.

```{r}
################################################
################## Q3: #########################
################################################

# What is the average order value (ABC) by Tier and Sub sector

q3 <- aggregate(dat$`ABC Amount`,by=list(dat$`Account Tier`,dat$`Sub Sector ID`),FUN=mean,na.rm=TRUE)
colnames(q3) <- c("Tier","SubSector","AverageOrder")
q3$Tier <- as.factor(q3$Tier)
plot4 <- ggplot(q3, aes(x = factor(SubSector), y = AverageOrder, fill = Tier)) +
  geom_bar(position = position_stack(), stat = "identity", width = .7) +
  geom_text(aes(label = round(AverageOrder,1)), position = position_stack(vjust = 0.5), size = 3.5)+theme(axis.text.x = element_text(angle = 45, hjust = 1))

plot4 <- plot4 + labs(title = "Average order value (ABC) by Tier and Sub sector",
                      y="Average", x = "Sub sector")
plot4


```

##Q4: What is average sales age by tier and sub sector.

```{r}
################################################
################## Q4: #########################
################################################


#What is average sales age by tier and sub sector

q3 <- aggregate(dat$`Sales Age`,by=list(dat$`Account Tier`,dat$`Sub Sector ID`),FUN=mean, na.rm=TRUE)
colnames(q3) <- c("Tier","SubSector","SalesAge")
q3$Tier <- as.factor(q3$Tier)
plot5 <- ggplot(q3, aes(x = factor(SubSector), y = SalesAge, fill = Tier)) +
  geom_bar(position = position_stack(), stat = "identity", width = .7) +
  geom_text(aes(label = round(SalesAge,1)), position = position_stack(vjust = 0.5), size = 3.5)+
  coord_flip()

plot5 <- plot5 + labs(title = "Average sales age by Tier and Sub sector",
                      y="Average", x = "Sub sector")
plot5


```


##Q5: For deals that have closed won what is the average sales age by tier and subsector.


```{r}

################################################
################## Q5: #########################
################################################

# For deals that have closed won what is the average sales age by tier and subsector

dat5 <- dat[dat$Stage == "Closed Won",]
q3 <- aggregate(dat5$`Sales Age`,by=list(dat5$`Account Tier`,dat5$`Sub Sector ID`),FUN=mean, na.rm=TRUE)
colnames(q3) <- c("Tier","SubSector","SalesAge")
q3$Tier <- as.factor(q3$Tier)
plot5 <- ggplot(q3, aes(x = factor(SubSector), y = SalesAge, fill = Tier)) +
  geom_bar(position = position_stack(), stat = "identity", width = .7) +
  geom_text(aes(label = round(SalesAge,1)), position = position_stack(vjust = 0.5), size = 3.5)

plot5 <- plot5 + labs(title = "Average sales age by Tier and Sub sector (Closed won)",
                      y="Average", x = "Sub sector")
plot5

# For deals that have closed lost what is the average sales age by tier and subsector
dat6 <- dat[dat$Stage == "Closed Lost",]
q3 <- aggregate(dat6$`Sales Age`,by=list(dat6$`Account Tier`,dat6$`Sub Sector ID`),FUN=mean, na.rm=TRUE)
colnames(q3) <- c("Tier","SubSector","SalesAge")
q3$Tier <- as.factor(q3$Tier)
plot5 <- ggplot(q3, aes(x = factor(SubSector), y = SalesAge, fill = Tier)) +
  geom_bar(position = position_stack(), stat = "identity", width = .7) +
  geom_text(aes(label = round(SalesAge,1)), position = position_stack(vjust = 0.5), size = 3.5)

plot5 <- plot5 + labs(title = "Average sales age by Tier and Sub sector (Closed lost)",
                      y="Average", x = "Sub sector")
plot5
```


##Q6: Number of deals closed by tier by opportunity owner.

```{r}

################################################
################## Q6: #########################
################################################





##################### Number of deals closed by tier by opportunity owner #########################


## Subsetting:
dat6 <- dat[dat$Stage == 'Closed Won',]


q1 <- with(dat6, ftable(dat6$`Opportunity Owner ID`,dat6$`Account Tier`))
q1 <- as.data.frame(q1)
colnames(q1) <- c("OpportunityOwner","Tier","Freq")
q1[q1 == 0] <- NA

q1$OpportunityOwner <- factor (q1$OpportunityOwner,
                        levels = c("Person1","Person2","Person6","Person7","Person8","Person9","Person10","Person11","Person13","Person14","Person15","Person16","Person17",
                                   "Person18","Person19","Person20", "Person21", "Person23", "Person24", "Person33"),ordered = TRUE)


plot6a <- ggplot(q1, aes(x = factor(OpportunityOwner), y = Freq, fill = Tier)) +
  geom_bar(position = position_stack(), stat = "identity", width = .7) +
  geom_text(aes(label = Freq), position = position_stack(vjust = 0.5), size = 3)+
  coord_flip()

plot6a <- plot6a + labs(title = "",
                      y="Number of deals closed won", x = "Opportunity owner")
plot6a



#########

dat6 <- dat[dat$Stage == "Closed Lost",]


q1 <- with(dat6, ftable(dat6$`Opportunity Owner ID`,dat6$`Account Tier`))
q1 <- as.data.frame(q1)
colnames(q1) <- c("OpportunityOwner","Tier","Freq")
q1[q1 == 0] <- NA

#nlevels(q1$OpportunityOwner)
q1$OpportunityOwner <- factor (q1$OpportunityOwner,
                               levels = c("Person1","Person2","Person3","Person5","Person6","Person7","Person8","Person9","Person12","Person13","Person14",
                                          "Person16","Person17","Person19","Person21","Person22","Person23","Person24","Person30",
                                          "Person31","Person32","Person33","Person34","Person35","Person36"),ordered = TRUE)


plot6b <- ggplot(q1, aes(x = factor(OpportunityOwner), y = Freq, fill = Tier)) +
  geom_bar(position = position_stack(), stat = "identity", width = .7) +
  geom_text(aes(label = Freq), position = position_stack(vjust = 0.5), size = 3)+
  coord_flip()

plot6b <- plot6b + labs(title = "",
                        y="Number of deals closed lost", x = "Opportunity owner")
plot6b







# library("ggpubr")
# figure6 <- ggarrange(plot6a,plot6b,ncol = 1, nrow = 2)
# 
# figure6 + labs(title = "Number of deals closed by tier by opportunity owner")


############### Total value (ABC) of deals closed by opportunity owner##################

dat6 <- dat[(dat$Stage %in% c("Closed Lost","Closed Won")),]


q6 <- aggregate(dat6$`ABC Amount`,by=list(dat6$Stage,dat6$`Opportunity Owner ID`),FUN=sum, na.rm=TRUE)

colnames(q6) <- c("Stage (closed)","Opportunity Owner","Total Value(ABC)")
# library(xtable)
# xtable(q6)
# 
# 
# 
# q6$`Opportunity Owner` <- factor (q6$`Opportunity Owner`,levels =c("Person1","Person2","Person3","Person5","Person6","Person7","Person8","Person9","Person10","Person11","Person12","Person13","Person14","Person15",                    "Person16","Person17","Person19","Person20","Person21","Person22","Person23","Person24","Person30",                                       "Person31","Person32","Person33","Person34","Person35","Person36"),ordered = TRUE)

```


\begin{table}[ht]
\centering
\caption{Total value (ABC) of deals closed by opportunity owner}{} 
\begin{tabular}{rllr}
  \hline
 & Stage & OpportunityOwner & TotalValue \\ 
  \hline
1 & Closed Lost & Person1 & 5400 \\ 
  2 & Closed Won & Person1 & 14817 \\ 
  3 & Closed Won & Person10 & 2760 \\ 
  4 & Closed Won & Person11 & 12600 \\ 
  5 & Closed Lost & Person12 & 9945 \\ 
  6 & Closed Lost & Person13 & 41630 \\ 
  7 & Closed Won & Person13 & 22861 \\ 
  8 & Closed Lost & Person14 & 3840 \\ 
  9 & Closed Won & Person14 & 3600 \\ 
  10 & Closed Won & Person15 & 63606 \\ 
  11 & Closed Lost & Person16 & 13840 \\ 
  12 & Closed Won & Person16 & 2640 \\ 
  13 & Closed Lost & Person17 & 16548 \\ 
  14 & Closed Won & Person17 &   0 \\ 
  15 & Closed Won & Person18 & 36150 \\ 
  16 & Closed Lost & Person19 & 2220 \\ 
  17 & Closed Won & Person19 & 2220 \\ 
  18 & Closed Lost & Person2 & 1800 \\ 
  19 & Closed Won & Person2 & 5820 \\ 
  20 & Closed Won & Person20 & 1140 \\ 
  21 & Closed Lost & Person21 &   0 \\ 
  22 & Closed Won & Person21 & 4200 \\ 
  23 & Closed Lost & Person22 & 2160 \\ 
  24 & Closed Lost & Person23 & 3600 \\ 
  25 & Closed Won & Person23 & 1080 \\ 
  26 & Closed Lost & Person24 & 1839 \\ 
  27 & Closed Won & Person24 & 6165 \\ 
  28 & Closed Lost & Person3 & 15600 \\ 
  29 & Closed Lost & Person30 & 38430 \\ 
  30 & Closed Lost & Person31 & 1518 \\ 
  31 & Closed Lost & Person32 & 2520 \\ 
  32 & Closed Lost & Person33 & 3600 \\ 
  33 & Closed Won & Person33 & 4050 \\ 
  34 & Closed Lost & Person34 & 10000 \\ 
  35 & Closed Lost & Person35 & 3000 \\ 
  36 & Closed Lost & Person36 & 20000 \\ 
  37 & Closed Lost & Person5 & 900 \\ 
  38 & Closed Lost & Person6 & 39712 \\ 
  39 & Closed Won & Person6 & 41559 \\
  
  40 & Closed Lost & Person7 & 12112 \\ 
  41 & Closed Won & Person7 & 1530 \\ 
  42 & Closed Lost & Person8 & 536834 \\ 
  43 & Closed Won & Person8 & 206583 \\ 
  44 & Closed Lost & Person9 & 1000 \\ 
  45 & Closed Won & Person9 & 8100 \\ 
   \hline
\end{tabular}
\end{table}


##Q7: What is our sweet spot - i.e. which subsector and tier are we winning most deals? Which sub sector and tier are we losing most deals?

\begin{description}
  \item[$\bullet$ Sweet spot] Subsector = Service Type 2 and Tier = 3. (Total closed won = 23).
  \item[$\bullet$ Losing spot] Subsector = Service Type 2 and Tier = 2. (Total closed lost = 32).
\end{description}

```{r}

#head(dat)
#clw <- dat[dat$Stage == "Closed Won",]
clw <- dat[dat$Stage == "Closed Lost",]

#table(clw$`Sub Sector ID`,clw$`Account Tier`)
```

